% \cite{ilo}
% NEW SITE ---------------------------------------------------------------------------------
\begin{thebibliography}{9}

  \bibitem{ilo}
  ILO - World Social Protection Report 2017-2019,
  \textit{4 billion people worldwide are left without social protection},
  \url{https://www.ilo.org/global/about-the-ilo/newsroom/news/WCMS_601903/lang--en/index.htm},
  2017.
  
  \bibitem{etherscan}
  Etherscan,
  \textit{Ethereum Transaction Chart},
  \url{https://etherscan.io/chart/tx},
  2017.

  \bibitem{worldometers}
  Worldometers,
  \textit{World Population Forecast (2020-2050)},
  \url{http://www.worldometers.info/world-population/},
  2017.  

  \bibitem{bitcoin}
  Satoshi Nakamoto,
  \textit{Bitcoin: A Peer-to-Peer Electronic Cash System},
  \url{https://bitcoin.org/bitcoin.pdf},
  2009.
  
  \bibitem{cammarden}
  Carmela Troncoso, Marios Isaakidis,George Danezis, Harry Halpin,
  \textit{Systematizing Decentralization and Privacy: Lessons from 15 Years of Research and Deployments, In Proceedings on Privacy Enhancing Technologies},
  De Gruyter Open,
  volume 2017,
  2017.

  \bibitem{omisego}
  David Knott,
  \textit{Construction of a Plasma Chain 0x1},
  \url{https://blog.omisego.network/construction-of-a-plasma-chain-0x1-614f6ebd1612},
  2017.
  
  \bibitem{gdpr}
  GDPR Info,
  \textit{General Data Protection Regulation},
  \url{https://gdpr-info.eu/},
  2018.  
  
  \bibitem{plasma}
  Joseph Poon and Vitalik Buterin, 
  \textit{Plasma: Scalable Autonomous Smart Contracts},
  \url{https://plasma.io/},
  2017.
  
 \bibitem{plasmamvp}
  Minimal Viable Plasma,
  \url{https://ethresear.ch/t/minimal-viable-plasma/426},
  2017.
  
  \bibitem{plasmacash}
  Plasma Cash,
  \url{https://ethresear.ch/t/plasma-cash-plasma-with-much-less-per-user-data-checking/1298},
  2017.
  
  \bibitem{ethereum}
  Ethereum,
  \url{https://ethereum.org},
  2014.

  \bibitem{eckzahlen}
  Deutsche Rentenversicherung,
  \textit{Wichtige Eckzahlen},
  \url{https://www.deutsche-rentenversicherung.de/Allgemein/de/Navigation/6_Wir_ueber_uns/02_Fakten_und_Zahlen/03_statistiken/wichtige_eckzahlen_node.html},
  2016.

  \bibitem{hackernoon}
  Andrew Tayo,
  \textit{Proof of work, or proof of waste?},
  \url{https://hackernoon.com/proof-of-work-or-proof-of-waste-9c1710b7f025},
  2017.  
  
  \bibitem{tendermint}
  Jae Kwon,
  \textit{Tendermint: Consensus without Mining},
  \url{https://tendermint.com/static/docs/tendermint.pdf},
  2014.
  
  \bibitem{tendermint_bench}
  Zach,
  \textit{Tendermint: Benchmarks},
  \url{https://github.com/tendermint/tendermint/wiki/Benchmarks},
  2018.
  
  \bibitem{iacr}
  Eli Ben-Sasson, Iddo Bentov, Yinon Horesh, Michael Riabzev,
  \textit{Scalable, transparent, and post-quantum secure computational
integrity},
  \url{https://eprint.iacr.org/2018/046.pdf},
  2018.
  
  \bibitem{ethereum_zksnarks}
  Christian Reitwiessner,
  \textit{zkSNARKs in a nutshell},
  \url{http://chriseth.github.io/notes/articles/zksnarks/zksnarks.pdf},
  2016.

  \bibitem{fraetz}
  Fabian Raetz,
  \textit{Aufbau und Funktionsweise des Bitcoin-Protokolls},
  2014.  

  \bibitem{nrjcoin}
  NRJ Coin Project,
  \textit{NRJ Coin Project},
  \url{https://github.com/nrjcoin-project},
  2014.

  \bibitem{erd}
  European Report on Development (ERD): Deutsches Institut für Entwicklungspolitik,
  \url{https://www.die-gdi.de/erd/},
  2018.
  
  \bibitem{hcms}
  Health as Human Capital: Theory and Implications A New Management Paradigm, HCMS Group,
  \url{http://www.hcmsgroup.com/wp-content/uploads/2012/05/WP01-HHC-Theory-and-Implications-2012-01-161.pdf},
  2012.
 
  \bibitem{gaslimit}
  etherscan.io: gaslimit chart,
  \url{https://etherscan.io/chart/gaslimit},
  2012. 

\end{thebibliography}

