\section*{Conclusion}

Although finding functioning scaling solutions regarding blockchain-systems is a wide topic and needs a lot of more research in general, the evaluations in this paper state that efficient solutions to improve or even replace existing systems can be built by using blockchain while maintaining financial and socio-cultural benefits.
Plasma has great potential to work as the technological scaling base specifically for social security systems based on blockchain. Taking into consideration several difficulties like data unavailability, other issues, and the large community working on this issues, it’s a stony path, but also a feasible one.
\newline

We at Asure believe that the future of social security and insurance will be defined by blockchain technologies in a decentralized way, which creates a whole new experience geared for the digital world. It can only be achieved by using a decentralized blockchain platform as the basis for creating a network, blockchain, platform, and protocol for any kinds of risks in the world. 
\newline

The concept of implementing social security via the blockchain is unique and offers an enormous potential to improve human life worldwide. The promotion of social security on Blockchain would bring more trust, satisfaction, freedom and world peace. Asure is conceptually open, and we believe that it is very well suited to serve as a fundamental platform for a very large number of social security solutions in the coming years.
\newline

With our token sale, we want a wide range of people to participate in this long-term journey and create a success story by changing how social security works in our new digital age. Be part of this journey, and join our Token Generation Event - we are looking forward to welcoming you aboard!
\newline\newline

\begin{table}[H]
\begin{tabular}{lp{.62\textwidth}l}
  Website & \url{https://asure.network}\\
  Twitter: & \url{https://twitter.com/asure_network}\\
  Telegram channel: & \url{https://t.me/asure_network}
\end{tabular}
\end{table} 