\section{Asure Platform}

The Asure platform consists of components that provide the network and protocol for the use and construction of social security systems, including the Client, SDKs, tools and frontend applications. The purpose of the platform is to create an ecosystem in which social security systems can be developed, tested, simulated, managed and productively used as quickly as possible.

\subsection{Client}
Main client is the entry point into the Asure network, capable of running a node. Nodes are connected to each other in a peer-to-peer network and relay new information by gossip protocol. Each node keeps a complete copy of a totally ordered sequence of events in the Asure blockchain. The nodes are used to form and operate the Asure network and ensure that the transactions are included in the Asure blockchain.

\subsection{Software Development Kits (SDKs) }
The SDK provides standardized features on which applications can be built. Our primary goal is to simplify the development of new ecosystem solutions so that they require little to no developer support.

\subsection{Tools}
The tools support the creation, testing, and simulation of created solutions on the Asure network and blockchain and speed up the development process.

\subsection{Frontend applications}
In order to achieve user acceptance, the blockchain standard applications are provided, such as blockchain-explorer, pool, mobile-apps (Android, iOS,) with a wallet to make the experience of mobile payments on a  global scale possible, as well as unlocking the full potential of mobile commerce.
