\section{Asure TGE}

The terms and conditions of the token sale as well will be described in a separate document.
The Asure TGE will happen in two rounds. The first round will take place in Fall 2018. The second round will happen later in 2019. Tokens will be ERC20 / ERC223 compatible and limited in supply by 100.000.000. In total, we will sell 45\% of all ASR tokens through the TGE. 

\begin{table}[H]
\begin{tabular}{lp{.6\textwidth}l}
  Token name & Asure Token \\  
  Ticker & ASR\\
  Token issuer & Asure Foundation\\
  Token type & ERC20 / ERC223 \\
  Token for sale & 45.000.000 ASR \\
  Total token supply & 100.000.000 ASR \\
  Accepted currencies & ETH \\
  Exchange Rate & 1 ASR = \$ 1.00 (ETH equivalent) \\
  Minimum Contribution & \$ 100 (ETH equivalent) \\\hline  
  
  Pre-Sale & tba 2019 \\
  Pre-Sale Cap & \$ 5.000.000 \\
  Pre-Sale Terms & First week 50\% bonus and after first week 25\% bonus \\\hline
  Main-Sale & tba 2019 \\  
  Main-Sale Cap & \$ 35.000.000 \\
  Main-Sale Terms & First week 15\% bonus \\\hline

  Listing & ASR tokens will be listed on crypto exchanges \\
  Token Holder Benefits & ASR token serves as the access to the Asure network \\
  Token Trade Limitation & Only Team and Advisors have vesting and sales lock-in periods \\
  Hint & All unsold tokens in public TGE  will be burned \\\hline  
  
  Hardcap & \$ 40.000.000
  
\end{tabular}
\caption{\label{tab:table-name}Token details}
\end{table}

\subsection{Token}

There are basically two types of customers that are primarily targeted by Asure:

Network-Validaters: 

The ASR-Token is used to validate the network and in return the validators receive transaction fees.

Service Providers:

The ASR token is the native utility token of the Asure protocol and provides access to the Asure platform and services. It is implemented as an Ethereum smart contract and supports the  ERC-20 / ERC-223 token standards. 
\newline
The ASR token serves as an incentive for service providers within the Asure platform to work correctly and as advertised wwin their SLA’s. Service providers must deposit ASR tokens which are retained in the event of non-compliance with the corresponding SLA. This is also commonly known as proof-of-stake algorithms. A service within the Asure protocol could be e.g. oracles, products, reinsurance and sales activity.\newline
Demand for ASR tokens will be created by the two following mechanisms: With the growth of the Asure platform, more service provider will need to stake ASR tokens. The more service provider earn with their services, the more ASR tokens must be staked.
The ASR token will be listed on crypto exchanges for public trading so that service providers of the Asure platform can buy and sell ASR tokens.
\newline\newline



\subsection{Token allocation}

It is very important that the community understands how the Asure’s funds are going to be invested in the future in order to contribute to the idea of creating a world with an open decentralized autonomous system. See below how the investments will be allocated. 

\begin{itemize}
\item \textbf{Phase 1:} 20\% of all ASR tokens will be generated.
\item \textbf{Phase 2:} 80\% of all ASR tokens will be generated.
\end{itemize}

\subsubsection{Phase 1}

In the second phase we will distribute 20\% of all ASR token.

\begin{table}[H]
\begin{tabular}{llp{.62\textwidth}l}
  10\% & Public Pre-Sale & Contributions will be used to develop the network mvp, and to build bigger community.\\
  5\% & Family \& Friends & Family and Friends receive their tokens as part of their compensation package.\\
  5\% & Bounty & Asure provides compensation for a number of tasks spread across marketing, bug reporting or even improving aspects of the Asure network, platform and protocol.
\end{tabular}
\caption{\label{tab:table-name} Phase 1 - Token allocation}
\end{table}

\subsubsection{Phase 2}

In the second phase we will distribute 80\% of all ASR token.

\begin{table}[H]
\begin{tabular}{llp{.62\textwidth}l}
  35\% & Public Main-Sale & Contributions will be used to develop the platform, and to fund security, legal and operational needs. \\
  35\% & Foundation & Comprises foundation development and education initiatives, incentives to developers and to research blockchain, scaling, network, platform and protocol.\\
  8\% & Team  & These are placed to acknowledge the time, effort and resources contributed to the Asure platform.  The Asure team receive their tokens as part of their compensation package, and team tokens will be vested.\\
  2\% & Advisors & Advisors receive their tokens as part of their compensation package.
\end{tabular}
\caption{\label{tab:table-name} Phase 2 - Token allocation}
\end{table}

\subsubsection{Vesting}
According to best practice and in order to protect investors and future participants of our platform, we will lock up our team’s tokens. The Asure Team will receive their tokens in twelve equal parts over two years.
The vesting ensures token course stability and commitment of all involved team members. If a holder attempts to transfer more ASR tokens than vested, the transaction will be blocked.
We are going to publish the smart contract to control vesting within our project. Hence, we will prove to the community our long-term commitment. 

\subsection{Funds allocation}

We envision that all ETH derived from the sale of Asure utility tokens ("ASR") will be allocated in the following manner:
\newline\newline

\begin{table}[H]
\begin{tabular}{llp{.6\textwidth}l}
  45\% & Platform R\&D & The creation of ongoing development of our Layer-2 network \\
  30\% & Marketing \& Operations & Additional staff and resources to cover day-to-day operations and prudent management as the organization expands. \\
  10\% & Legal & We are acutely aware of the need for rigorous compliance. We will need our own well-resourced legal support. Our principal concern is to fit within complex regulatory frameworks across the globe in order to make the growth of the community legally secure. \\
  10\% & Tax & Tax and organization development fees.\\
  5\% & Office Expenses & Office expenses and HR activities to build up
        a team to achieve roadmap goals
\end{tabular}
\caption{\label{tab:table-name}Funds allocation}
\end{table}

\subsection{KYC/AML}

The primary objective of token sale registration is to enforce a mandatory Know-Your-Customer (KYC) check to prevent identity theft, terrorist financing, Anti-money laundering (AML), and financial fraud. It also allows our team to understand our token holders better and manage risks appropriately.

The Asure tokens are not being offered or distributed to, as well as cannot be resold or otherwise alienated by their holders to citizens of, natural and legal persons, having their habitual residence, location or their seat of incorporation in the country or territory where transactions with digital coins are prohibited or in any manner restricted by applicable laws or regulations, or will become prohibited or restricted at any time after this agreement becomes effective (“Restricted Persons”).

We do not accept participation from the restricted persons and reserve the right to refuse or cancel the ASR token purchase requests at any time at our sole discretion when the information provided by the purchasers within the KYC procedure is not sufficient, inaccurate or misleading, or the purchaser is deemed to be a restricted person.

\subsection{Privacy and Security}
The security of your data is of great importance to us. There is no “cutting corners” when it comes to security, even under the pressure of running an ICO.  As such, please find below the measures which will be employed to ensure your privacy and security: 

All your data will be stored in an encrypted form on our servers
We don’t store your password as we only support external authentication providers like Google and Facebook
All the information required for the KYC process will be wiped out from our systems once the checks are completed

Asure will never share members’ personal data with 3rd parties without prior consent. In order to be on the safe side you should take these precautions: 

Never send any fiat money or crypto coins to any address during the registration process. There is only one public token sale date and it is specified on our 
website: https://www.asure.network
Bookmark the registration website, and never get to it following any email links.
Never trust emails related to the particular sale details (such as the information about soft or hard caps, Ethereum address to send to, etc.). Remember that sender’s email address can be easily forged. 
Never reply to our emails. Perform all your operations on our website only. You can check your registration status on our website using your account details. 


\subsection{Excluded participants}
Due to legal restrictions citizens and residents from the following countries are not eligible to acquire ASR tokens: American Samoa, Belarus, Burundi, Central African Republic, Cuba, Congo (Brazzaville), Congo (Kinshasa), Guam, Iraq, Iran, Lebanon, Libya, Northern Mariana Islands, North Korea, Puerto Rico, Somalia, Sudan, South Sudan, Syria, United States, US Virgin Islands, US Minor Outlying Islands, Venezuela, Yemen, Zimbabwe.
