\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{url}
\usepackage{float}
\usepackage{color} 
\usepackage[sort=use]{glossaries-extra}

%\definecolor{pagecolor}{rgb}{0.8,0.9,0.9}

\usepackage[tocflat]{tocstyle}
\usetocstyle{standard}

\newglossaryentry{blockchain}{name={Blockchain},plural={Blockchains},
description={A system in which a record of transactions are maintained across several computers that are linked in a peer-to-peer network.}}
\newglossaryentry{ethereum}{name={Ethereum},plural={Ethereum},
description={A decentralized software platform that enables SmartContracts and Distributed Applications (ĐApps).}}
\newglossaryentry{eth}{name={ETH},plural={eth},
description={Native token of the Ethereum blockchain.}}
\newglossaryentry{btc}{name={BTC},plural={BTC},
description={Native token of the Bitcoin blockchain.}}
\newglossaryentry{erc20}{name={ERC20},plural={ERC20},
description={A technical standard used for smart contracts on the Ethereum blockchain for implementing tokens.}}
\newglossaryentry{smartcontract}{name={SmartContract},plural={SmartContract},
description={A smart contract is a computer protocol intended to digitally facilitate, verify, or enforce the negotiation or performance of a contract. Smart contracts allow the performance of credible transactions without third parties. These transactions are trackable and irreversible.}}
\newglossaryentry{account}{name={Account},plural={accounts},
description={A hash of a public key which can hold values. Hold values can only be accessed by knowing the corresponding private key.}}
\newglossaryentry{gdpr}{name={GDPR},plural={GDPR},
description={The General Data Protection Regulation (EU) 2016/679 ("GDPR") is a regulation in EU law on data protection and privacy for all individuals within the European Union (EU).}}
\newglossaryentry{payg}{name={PAYG},plural={PAYG},
description={a method of financing social insurance, especially old-age provision, but also health insurance and unemployment insurance. The paid-in contributions are used directly to finance the beneficiaries, ie they are paid back to them.}}


\begin{document}

%\pagecolor{pagecolor}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\clearpage

\input{_head}

\pagenumbering{arabic}% Arabic page numbers (and reset to 1)
\newpage

\input{_abstract}

% list all entries
\printunsrtglossaries
\newpage
\tableofcontents

\newpage
% NEW SITE ---------------------------------------------------------------------------------
\input{_introduction}

%\input{_decentralized_social_security}
%\newpage
\input{_network}

%\newpage
\input{_blockchain}

\input{_platform}

%\newpage

%\input{_tge}

\input{_past_work}

\newpage

\input{_future_work}

\input{_organisation}

\input{_acknowledgements}

\input{_conclusion}

\newpage

\listoftables

\listoffigures
 
\newpage
% Literaturliste endgueltig anzeigen
\input{_bibliography}
\bibliographystyle{ieeetr}
%\bibliography{literatur}



\vskip 2.2in
\begin{quote}
	\centering
	Made with \ensuremath\heartsuit{ }in Germany 
\end{quote}

\end{document}
