% \cite{ilo}
% NEW SITE ---------------------------------------------------------------------------------
\begin{thebibliography}{9}

  \bibitem{ilo}
  World social protection report 2017-2019,
   \textit{Universal social protection to achieve the sustainable development goals},
  International Labour Office, Geneva,
  2nd edition,
  2017.

  \bibitem{worldometers}
  Worldometers,
  \textit{World Population Forecast (2020-2050)},
  \url{http://www.worldometers.info/world-population/},
  2017.  

  \bibitem{bitcoin}
  Satoshi Nakamoto,
  \textit{Bitcoin: A Peer-to-Peer Electronic Cash System},
  \url{https://bitcoin.org/bitcoin.pdf},
  2009.
  
  \bibitem{cammarden}
  Carmela Troncoso, Marios Isaakidis,George Danezis, Harry Halpin,
  \textit{Systematizing Decentralization and Privacy: Lessons from 15 Years of Research and Deployments, In Proceedings on Privacy Enhancing Technologies},
  De Gruyter Open,
  volume 2017,
  2017.

  
  \bibitem{gdpr}
  GDPR Info,
  \textit{General Data Protection Regulation},
  \url{https://gdpr-info.eu/},
  2018. 
  
  \bibitem{ethereum}
  Ethereum,
  \url{https://ethereum.org},
  2014.

  \bibitem{eckzahlen}
  Deutsche Rentenversicherung,
  \textit{Wichtige Eckzahlen},
  \url{https://www.deutsche-rentenversicherung.de/Allgemein/de/Navigation/6_Wir_ueber_uns/02_Fakten_und_Zahlen/03_statistiken/wichtige_eckzahlen_node.html},
  2016.

  \bibitem{fraetz}
  Fabian Raetz,
  \textit{Aufbau und Funktionsweise des Bitcoin-Protokolls},
  2014.  

  \bibitem{nrjcoin}
  NRJ Coin Project,
  \textit{NRJ Coin Project},
  \url{https://github.com/nrjcoin-project},
  2014.

  \bibitem{erd}
  European Report on Development (ERD): Deutsches Institut für Entwicklungspolitik,
  \url{https://www.die-gdi.de/erd/},
  2018.
  
  \bibitem{hcms}
  Health as Human Capital: Theory and Implications A New Management Paradigm, HCMS Group,
  \url{http://www.hcmsgroup.com/wp-content/uploads/2012/05/WP01-HHC-Theory-and-Implications-2012-01-161.pdf},
  2012.
 

\end{thebibliography}

