\begin{abstract}

Research results show that social security plays a central role in economic and political development in developing countries. Empirical studies suggest that the existence of social security systems, especially in the informal sector, strengthens the propensity to invest and thus promotes economic growth precisely where this best contributes to poverty reduction. 

Worldwide, there are over 4.1 billion people without access to social security systems. At Asure, we’re working towards a future in which all people have access to social security systems. Together with the governments around the world, Asure is improving existing social security systems and is introducing them to reduce poverty and illness.
Through technical achievements such as the Internet, smartphones, cryptocurrencies and blockchain technology, we will also succeed in emerging markets. The Blockchain technology plays a key role in our vision in this respect.

The Blockchain technology offers many advantages which form an ideal foundation for modern social security systems. Among the advantages are durability, reliability, longevity, process integrity, transparency, immutability, ecosystem simplification, lower transaction costs, and a high degree of automation. The big challenge as of today is, that blockchain technologies do not scale. In order to solve the scaling problem in the future, many blockchains will be used for application-specific cases and these will be connected in such a way that assets can be transferred back and forth between chains.
\newline\newline

\textbf{Note:} asure.network is a work in progress. Active research is under way, and new versions of this paper will appear at http://asure.network
For comments and suggestions, contact us at research@asure.network.

\end{abstract}


\newpage
% NEW SITE ---------------------------------------------------------------------------------