\section{Future Work}

This work presents a clear and cohesive path toward the construction of the Asure network; however, we also consider this work to be a starting point for future research on decentralized social security systems. In this section we identify and populate three categories of future work. This includes work that has been completed and merely awaits description and publication, open questions for improving the current protocols, and formalization of the protocol.

\subsection{On-going Work}

The following topics represent ongoing work.

\begin{itemize}
\item Decentralized social security system.
\item Plasma MVP implementation.
\item Asure-in-Ethereum interface contracts and protocols.
\item A full implementable Asure protocol specification.
\end{itemize}

An Asure Foundation is established for the development and research of further social security systems on blockchain and the decentralisation of these.

\begin{itemize}
\item \textbf{Health care}
\item \textbf{Unemployment insurance}
\item \textbf{Accident insurance}
\item \textbf{Nursing insurance}
\end{itemize}

\subsection{Open Questions}

There are a number of open questions whose answers have the potential to substantially improve the network as a whole, despite the fact that none of them have to be solved before launch.

\begin{itemize}
\item Social security systems and economy models.
\item A better primitive for the Proof-of-Stake Prove function, which is publicly-verifiable and transparent.
\end{itemize}