\section{Future work}
The present work aimed to develop a concept of a decentralized pension. In closing, it can be noted that there are still open issues to be discussed.

\paragraph{SmartContract system.} The next step is to implement the specification of the proposed pension system as a SmartContract system using a blockchain (Ethereum) and make it available to the community for review.

\paragraph{Use of stablecoins.} The system still lacks an evaluation of the effects of the volatility of cryptocurrencies like ETH and BTC and if the use of stablecoins would be beneficial. 

\paragraph{Release unused pensions.} It is assumed that some users will opt for an earlier pension, even if it means partial loss for a user. Some users will lose full access to the system because e.g. the private key is lost, the pension contributions are not inherited and not collected. After some time, the paid-in values could be released, which will benefit the other users in the system. Further research of these conditions has to be done.

\paragraph{Liability, Governance.} The question of the liability and control of the system is not yet fully clarified.

\paragraph{Asset management.} In addition to a pure pay-as-you-go system, deposits can be made directly into the system, which involves both risks and reward opportunities, and for those who are more interested in risks, such research and results would be of great interest.

\paragraph{Scalable network.} In order operate a global pension system or any other social security system, it is necessary to have a scalable blockchain network at hand which could handle a large amount of transactions and supports further requirements that those these system need.

\paragraph{Reset.} It would be interesting to reset the pension system in case it runs into a dead end (e.g. no new contributors are joining the system and all pensions are paid).

\paragraph{Other use cases.} In addition to decentralized pension, other social insurances may also be decentralized, such as: health insurance, accident insurance, unemployment insurance etc. In addition to the well-known social insurance, the future and unconditional basic income can be organized decentrally.