\documentclass[10pt,twocolumn]{article}
%\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{breqn}
\usepackage{cite}
\usepackage[sort=use]{glossaries-extra}

\usepackage{titlesec}
\usepackage{lipsum}% provides filler text

\titlespacing{\paragraph}{%
  0pt}{%left margin
  0.1\baselineskip}{% space before (vertical)
  0.1em}%space after (horizontal)
\setlength{\parindent}{0em}
\setlength{\parskip}{1.0em}

\newglossaryentry{blockchain}{name={Blockchain},plural={Blockchains},
description={A system in which a record of transactions are maintained across several computers that are linked in a peer-to-peer network.}}
\newglossaryentry{ethereum}{name={Ethereum},plural={Ethereum},
description={A decentralized software platform that enables SmartContracts and Distributed Applications (ĐApps).}}
\newglossaryentry{eth}{name={ETH},plural={eth},
description={Native token of the Ethereum blockchain.}}
\newglossaryentry{btc}{name={BTC},plural={BTC},
description={Native token of the Bitcoin blockchain.}}
\newglossaryentry{erc20}{name={ERC20},plural={ERC20},
description={A technical standard used for smart contracts on the Ethereum blockchain for implementing tokens.}}
\newglossaryentry{smartcontract}{name={SmartContract},plural={SmartContract},
description={A smart contract is a computer protocol intended to digitally facilitate, verify, or enforce the negotiation or performance of a contract. Smart contracts allow the performance of credible transactions without third parties. These transactions are trackable and irreversible.}}
\newglossaryentry{account}{name={account},plural={accounts},
description={A hash of a public key which can hold values. Hold values can only be accessed by knowing the corresponding private key.}}
\newglossaryentry{gdpr}{name={GDPR},plural={GDPR},
description={The General Data Protection Regulation (EU) 2016/679 ("GDPR") is a regulation in EU law on data protection and privacy for all individuals within the European Union (EU).}}
\newglossaryentry{payg}{name={PAYG},plural={PAYG},
description={a method of financing social insurance, especially old-age provision, but also health insurance and unemployment insurance. The paid-in contributions are used directly to finance the beneficiaries, ie they are paid back to them.}}
\newglossaryentry{cpr}{name={CPR},plural={CPR},
description={The contribution pension rate  defines the conversion rate from DPT to contributions.}}
\newglossaryentry{dpt}{name={DPT},plural={DPT},
description={Decentralized pension tokens represent the contributed amounts relative to all other contributions of a given period.}}
\newglossaryentry{ppi}{name={PPI},plural={PPI},
description={The purchasing power index represents the reference value for a \gls{dpt}¸ of the corresponding period.}}

\begin{document}  
	%\renewcommand{\baselinestretch}{0.4}\normalsize
	
    \input{_title}
	\newpage
	\input{_abstract}	
	

	%\tableofcontents


    \input{_introduction}
    \input{_spec-payment}
	\input{_spec-payout}
    \input{_simulations}   
    \input{_conclusion}
    \input{_futurework}

	%\input{_bibliography}
	\bibliography{_bibliography}{} 	% Literaturliste endgueltig anzeigen
	\bibliographystyle{plain}
	%\onecolumn
	
 	% list all entries
	\printunsrtglossaries

	%\vskip 2.2in
	\begin{quote}
	%\centering
		\quad\quad\quad\quad Made with decentralized 		 \ensuremath\heartsuit{ }
	\end{quote}
\end{document}